Compiling refinement types to dependent types

### 2020-07-20 tex/paper.tex
Add a nonterm for core types
Add a TWF rule for ADTs
Proof of well-typedness preservation becomes trivial at least

\newNTclass{nonterm}
\newnonterm e \varepsilon
\newnonterm{es}{\varepsilon}
\newnonterm{ec}{\hat\varepsilon}
\newnonterm r \rho
\newnonterm{ts}{\tau}
\newnonterm s s
\newnonterm l l
\newnonterm B B
\newnonterm G \Gamma
\newnonterm{GC}{\hat\Gamma}
\newnonterm{binop}{\odot}

@@

\begin{figure}[ht]
  \footnotesize
  \drules[TCTX]{$\nonterm G \text{ ok}$}{context well-formedness}{Empty,Bind}
  \drules[TWF]{$\nonterm G \vdash \nonterm{ts}$}{type well-formedness}{TrueRef,Base,Conj,Arr}
  \drules[T]{$\nonterm G \vdash \nonterm{es} : \nonterm{ts}$}{term typing}{Unit,Var,Abs,App,Case,Con,Sub}
  \drules[ST]{$\nonterm G \vdash \nonterm{ts}_1 <: \nonterm{ts}_2$}{subtyping}{Base,Arr}
  \caption{Surface language typing}
  \label{fig:surface_typing}
\end{figure}

@@

\begin{theorem}[Well-typedness preservation]
  For any well-typed surface language term $\nonterm{es}$,
  the result of the translation $\tranterm(\nonterm{es})$ is ``equivalently'' typeable in the core language:
  \[
    \nonterm G \vdash \nonterm{es} : \nonterm{ts} \implies \tranctx(\nonterm G) \vdash \tranterm(\nonterm{es}) : \tranty(\nonterm{ts})
  \]
\end{theorem}
\begin{proof}
  We prove this by induction on the derivation of the typeability of $\nonterm{es}$.
  In particular, we consider the last typing rule used:
\end{proof}

>>>>

\newNTclass{nonterm}
\newnonterm e \varepsilon
\newnonterm{es}{\varepsilon}
\newnonterm{ec}{\hat\varepsilon}
\newnonterm r \rho
\newnonterm{ts}{\tau}
\newnonterm{tc}{\hat\tau}
\newnonterm s s
\newnonterm l l
\newnonterm B B
\newnonterm G \Gamma
\newnonterm{GC}{\hat\Gamma}
\newnonterm{binop}{\odot}

@@

\begin{figure}[ht]
  \footnotesize
  \drules[TCTX]{$\nonterm G \text{ ok}$}{context well-formedness}{Empty,Bind}
  \drules[TWF]{$\nonterm G \vdash \nonterm{ts}$}{type well-formedness}{TrueRef,Base,Conj,Arr,Rec}
  \drules[T]{$\nonterm G \vdash \nonterm{es} : \nonterm{ts}$}{term typing}{Unit,Var,Abs,App,Case,Con,Sub}
  \drules[ST]{$\nonterm G \vdash \nonterm{ts}_1 <: \nonterm{ts}_2$}{subtyping}{Base,Arr}
  \caption{Surface language typing}
  \label{fig:surface_typing}
\end{figure}

@@

\begin{theorem}[Well-typedness preservation]
  For any well-typed surface language term $\nonterm{es}$,
  the result of the translation $\tranterm(\nonterm{es})$ is ``equivalently'' typeable in the core language.
\end{theorem}
\begin{proof}
  This follows directly from the definition of $\tranterm$ via $\Tranterm$,
  the latter being total and mapping onto typing derivations in the core language.
\end{proof}
